Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-12 paper.tex
Qualify what high solidity means; resolves #63

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$, where $U_\infty$ is the
free stream velocity, $c$ is the blade chord length, $\nu$ is the fluid
kinematic viscosity, $\omega$ is the rotor's angular velocity, and $R$ is the
rotor radius. The value of $\lambda$ at which a turbine reaches peak performance
in general decreases with turbine solidity $Nc/\pi D$, which allows for the use
of a simpler Reynolds number based on turbine diameter $Re_D \equiv U_\infty
D/\nu$.

>>>>

The performance and wake characteristics of cross-flow (vertical-axis) turbines
depend on turbine solidity, blade profile (lift/drag, dynamic stall at reduced
frequency of turbine rotation, symmetry, thickness, camber), blade pitch, number
of blades, strut drag and operational parameters such as tip speed ratio---{\em
    and} on Reynolds number. Note that an average blade chord Reynolds number,
$Re_{c,\mathrm{avg}} \approx \lambda U_\infty c/ \nu$, can be expressed in terms
of tip speed ratio $\lambda \equiv \omega R/ U_\infty$, where $U_\infty$ is the
free stream velocity, $c$ is the blade chord length, $\nu$ is the fluid
kinematic viscosity, $\omega$ is the rotor's angular velocity, and $R$ is the
rotor radius. The value of $\lambda$ at which a turbine reaches peak performance
in general decreases with turbine solidity $Nc/(\pi D)$ \cite{Templin1974},
which allows for the use of a simpler Reynolds number based on turbine diameter
$Re_D \equiv U_\infty D/\nu$.

Solidity often directly correlates with the chord-to-radius ratio $c/R$. Rotors
with $c/R \ge 0.1$ are considered high solidity \cite{Fiedler2009}, for which
so-called flow curvature or virtual camber effects become significant
\cite{Migliore1980}. These effects arise from the blade sections' circular
paths, and can complicate the comparison with behavior of an airfoil in a linear
flow.
